\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-11 paper/subdocuments/data_and_methods.Rnw
minor changes method section

% What about the DELL Study, where high share of non-fillers are reported? What are the reasons?

@@

\emph{Measuring inequality or concentration} \\
To be able to make qualifying statements about a distribution or to compare different distributions, the concept of inequality turned out to be the most appropriate and thus the most commonly used dimension. See \citet{Allison 1978 FEHLT}, \citet{engelhardt_modelle_2000}, \citet{cowell_chapter_2000} and \citet{hao_assessing_2010}.
%[Zusammenfassung bestehender Überlegung und Hinleitung zu den Masszahlen, die wir verwenden werden (vermutlich Gini und relative distribution methods) \\

neuere Indikatoren; Polaritätsindex: relative distribution methods in the Social Sciences \citep{handcock_relative_1999} \\

The Gini coefficient is mainly used for international comparison. However, other measures are often reported along because the Gini coefficient is more sensitive to changes in the middle of the distribution than to changes in the tails \citep[37]{OECD, 2008 FEHLT}. Newer branches of inequality studies emphasize the need for broader measures of inequality, which allow better analyses about the change of inequality and namely statements about the area of change (downgrading/upgrading) \citep{Alderson and Doran 2013 FEHLT}. \\

\citet{Alvaredo (2010) FEHLT} shows formally, how top incomes shares are related to the Gini-coefficient. Following his argument, it is crucial to consider top incomes. \citet{leigh_how_2007} also analyzed the relationship between the Gini (and further inequality measures) and top income shares in a panel of 13 countries (Switzerland is part of the study). 
%[He also discusses tax data studies in general-> have a closer look] \\
%[We definitely have to argue, why it isn’t sufficient to report top income shares, because if it is, there is no need to have another study about Switzerland (national level>Martinez, cantonal level> gorgas and Schaltenegger)]

@@

%[ich stelle mir eine Tabelle mit verschiedenen Dimensionen vor, anhand derer eine Einordnung unterschiedlicher Datenquellen geschieht.]
% Mögliche Vergleichsdimensionen
%- Suitability of cross country comparison
%- Coverage of the population of interesst
%- Implementation of common concepts of economic ressources
%- contingency for intertemporal comparision

@@

@@

% 3. Eigenheiten Steuereinheiten

@@

See for other countries: \citealt{Siminski et al 2003 FEHLT} (Australia), \citealt{Brewer et al 2008 FEHLT}, UK, \citealt{Burkhauser et al. 2009 FEHLT}, US)
%	•	What about the special cases? Foelmi and Martinez argue, that it is crucial to include the special cases because they include the high net wealth individuals taxed according to their expenditures. Exclusion leads to an underestimation of inequality
%	•	Capital gains? Should not be included 
The discussion about problems with reporting income is fairly exhaustive. What about wealth?

It is well recognized that the traditional sources of wealth distribution data are unlikely to provide an accurate picture of wealth ownership in the top-tail of the distribution. \citet{credit_suisse_global_2011} makes use of the information in the ``Rich Lists'' published by Forbes Magazine to adjust the wealth distribution pattern in the highest wealth ranges. \\

Additionally the Credit Suisse Reports states that these data my be less subject to response bias, but my be more prone to valuation problems, especially in connection with pension assets and debts \citep[8]{credit_suisse_global_2011}.

@@

@@

>>>>

% What about the DELL Study, where high share of non-fillers are reported? What are the reasons?
% Bisher nirgends erwähnt ist die Kritik an Steuerdaten bezüglich tax avoidance and tax evasion.

@@

\emph{Measuring inequality or concentration} \\
To be able to make qualifying statements about a distribution or to compare different distributions, the concept of inequality turned out to be the most appropriate and thus the most commonly used dimension. See \citet{Allison 1978 FEHLT}, \citet{engelhardt_modelle_2000}, \citet{cowell_chapter_2000} and \citet{hao_assessing_2010}. The Gini coefficient is mainly used for international comparison. However, other measures are often reported along because the Gini coefficient is more sensitive to changes in the middle of the distribution than to changes in the tails \citep[37]{OECD, 2008 FEHLT}. Newer branches of inequality studies emphasize the need for broader measures of inequality, which allow better analyses about the change of inequality and namely statements about the area of change (downgrading/upgrading) \citep{Alderson and Doran 2013 FEHLT}.
%[Zusammenfassung bestehender Überlegung und Hinleitung zu den Masszahlen, die wir verwenden werden (vermutlich Gini und relative distribution methods) \\

%\citet{Alvaredo (2010) FEHLT} shows formally, how top incomes shares are related to the Gini-coefficient. Following his argument, it is crucial to consider top incomes. \citet{leigh_how_2007} also analyzed the relationship between the Gini (and further inequality measures) and top income shares in a panel of 13 countries (Switzerland is part of the study). 
%[He also discusses tax data studies in general-> have a closer look] \\
%[We definitely have to argue, why it isn’t sufficient to report top income shares, because if it is, there is no need to have another study about Switzerland (national level>Martinez, cantonal level> gorgas and Schaltenegger)]

@@

%[ich stelle mir eine Tabelle mit verschiedenen Dimensionen vor, anhand derer eine Einordnung unterschiedlicher Datenquellen geschieht.]
% Mögliche Vergleichsdimensionen
%- Suitability of cross country comparison
%- Coverage of the population of interesst
%- Implementation of common concepts of economic ressources
%- contingency for intertemporal comparision
%- flexibel applications of appropriate inequality measures

@@

% Die Punkte kurz beschreiben.

@@

@@

% Könnte man in der Introduction platzieren.

See for other countries: \citealt{Siminski et al 2003 FEHLT} (Australia), \citealt{Brewer et al 2008 FEHLT}, UK, \citealt{Burkhauser et al. 2009 FEHLT}, US)
%	•	What about the special cases? Foelmi and Martinez argue, that it is crucial to include the special cases because they include the high net wealth individuals taxed according to their expenditures. Exclusion leads to an underestimation of inequality
%	•	Capital gains? Should not be included

@@

% Diese Abschnitt muss ersetzt werden mit der von uns gewählten Vorgehensweise

@@

%The discussion about problems with reporting income is fairly exhaustive. What about wealth?

%It is well recognized that the traditional sources of wealth distribution data are unlikely to provide an accurate picture of wealth ownership in the top-tail of the distribution. \citet{credit_suisse_global_2011} makes use of the information in the ``Rich Lists'' published by Forbes Magazine to adjust the wealth distribution pattern in the highest wealth ranges. \\

%Additionally the Credit Suisse Reports states that these data my be less subject to response bias, but my be more prone to valuation problems, especially in connection with pension assets and debts \citep[8]{credit_suisse_global_2011}.
